Title

### 2023-06-01 main.tex
added super-widget 2.0.

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Acá te falto la puntuación en las ecuaciones. Porotro lado me gustaría ver la 
forma que tienen las ecuaciones en exponenciales o en funciones trigonometricas
que quizá estén mas bonitas.}
\tbnote{Ya puse la puntuación y lo puse en términos de arctan.
La suma de arcotangentes se puede juntar en una 
sola arctan, pero con un argumento que ya queda muy complicado y 
creo que está mejor así.}

@@

We took a sample of one-qubit Pauli channels and
used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
to simulate them. \cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
la frase.}
\tbnote{Ya.}  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this operator with the ideal 
channel $\xi_T$  we
wanted to implement.

\cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa es 
la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire alrededor de ella. }

\tbnote{Rediseño párrafo anterior: }
{\color{orange}  We took a sample of one-qubit Pauli channels
and evaluated their implementation on IBM's
ibmq-lima quantum computer~\cite{Qiskit},
as shown in \fref{fig:fids}. 
For each of the channels sampled, we used 
quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit in the quantum computer. 
Then, we compared $\xi_I$ with the theoretical 
operator $\xi_T$ of the Pauli channel we wanted to implement.
To see how close the operators $\xi_I$ and 
$\xi_T$ are, we shall use the
diamond distance~\cite{Aharonov,Wilde}, which is defined by}

%We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
%with the probability that one can distinguish two channels.
%In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
%with probability $1/2$ each,
%and tries to guess which channel they received
%by applying it to a state $\rho$ and measuring the result.
%Then, the maximal probability of success (out of all possible states $\rho$) that
%the agent guesses correctly is~\cite{Benenti}:
%\begin{equation}
%\label{eq: probability-success}
%p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
%\end{equation}
%where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by

\begin{align*}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{align*}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
{\color{orange} The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.}
\cpnote{Esa definicion esta bonita y me gusta, pero supongo qeu no es asi somo la 
calculas. } 
\tbnote{La calculo usando una función en la librería de Qiskit
que se basa en la referencia que puse,
pero la verdad no sé bien cómo funciona.}

%Notice that if the channels are the same, then $p_{\succ}=1/2$. 
%This is expected because in this situation the agent
%has no way of distinguishing the channels and has no choice but to completely
%guess, which results in a probability of success of $1/2$.
%On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
%distinguishable.
\cpnote{Creo qeu el ejemplo debería ir con la $f$ que definamos, quizá pasando por la 
norma diamante, o por la p succ. Eso si, si no la ocupamos (la psucc) tonces quitarla.}
\tbnote{Va, ya puse directo con la $f$ y quité lo de psucc}

{\color{orange} When the two channels are the same,
the diamond distance has a value of $0$, while in the case that the channels
are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as:

\begin{align}
f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
\label{eq:diamond-fid}
\end{align}
which is a number between $0$ and $1$,
with $1$ indicating that the channels are completely
equal and $0$ the opposite.
}
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a high $f$, while those 
close to unitary channels have much lower $f$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes.
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}
\tbnote{Va}

\begin{figure}
\centering
\begin{subfigure}{0.9\textwidth}
\begin{subfigure}{.666\textwidth}
\centering
\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
\end{subfigure}%
\begin{subfigure}{.333\textwidth}
\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
\end{subfigure}
\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
\end{subfigure}%
\begin{subfigure}{0.1\textwidth}
\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
\end{subfigure}
\caption{\cpnote{porfa escribe el caption.} \tbnote{Aquí está una forma
alternativa en que puede quedar la figura.  Usé $2(1-p_{succ})$ en lugar de
$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.} Results of the diamond fidelities as defined in \eref{eq:diamond-fid} for a sample of Pauli channels in the tetrahedron.
Notice that channels close to the center of the tetrahedron have high fidelities,
while those close to the borders do not. 
Moreover, we show the results for cuts of the tetrahedron at different values of $\tau_3$.}
\label{fig:fids}
\end{figure}

@@

\begin{theorem}
Consider a 1PR circuit of $N$ qubits
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
\end{align*}
with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $|a^j|^2 + |b^j|^2 + |c^j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
\cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
\tbnote{La cambié un poco, pero no sé qué más cambiarle.}
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
with $B_{i,j}$ the entries of matrix $B$.
This can be rewritten by separating last qubit from the other $N-1$:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{align}
B|j\rangle = \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right),
\end{align}
Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is} |\mathfrak{b}^{j}\rangle + e^{is} |\mathfrak{a}^j\rangle + |\mathfrak{c}^j\rangle
\end{align}
where we defined $|\mathfrak{a}^j \rangle = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
$|\mathfrak{b}^j\rangle = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle$,
$|\mathfrak{c}^j\rangle =\sum_{k \not\in \mathcal{C}}\big( B_{2k,j} |k\rangle|0\rangle+$ $B_{2k+1,j} |k \rangle |1\rangle  \big)$.
\cpnote{Preferira que tuvieramos que los kets fisicos tuvieran la notacion de
ket. Intenta modificarlo asi y luego sigo con la prueba. Ya no me está pareciendo 
tan latosa. Trata tambien que los nombres que usas sean como consistentes o tengan 
algo que decir de su contenido.} \tbnote{Ya hice unos cambios}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $|\mathfrak{a}^j|^2 + |\mathfrak{b}^j|^2 + |\mathfrak{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

@@

@@

%Therefore, from this theorem we conclude that
%the kind of curves of states that can be created
%using a 1PR circuit are always of the form
%\begin{align*}
%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
%\end{align*}
%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
% }}}
\section{1PR circuit for a Pauli map} % {{{
\label{sec: 1PR circuit for a Pauli map}

>>>>

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
quizá tambien sean sencillas. Las quiero ver!!!}

@@

We took a sample of one-qubit Pauli channels and
used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
to simulate them. For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this operator with the ideal 
channel $\xi_T$  we
wanted to implement.

% \cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa
% es la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire
% alrededor de ella. }

% \tbnote{Rediseño párrafo anterior: }
% {\color{orange}  
We took a sample of one-qubit Pauli channels
and evaluated their implementation on IBM's
ibmq-lima quantum computer~\cite{Qiskit},
as shown in \fref{fig:fids}. 
For each of the channels sampled, we used 
quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit in the quantum computer. 
Then, we compared $\xi_I$ with the theoretical 
operator $\xi_T$ of the Pauli channel we wanted to implement.
To see how close the operators $\xi_I$ and 
$\xi_T$ are, we shall use the
diamond distance~\cite{Aharonov,Wilde}, which is defined by
\begin{equation}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{equation}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
When the two channels are the same,
the diamond distance has a value of $0$, while in the case that the channels
are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
\begin{equation}
f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
\label{eq:diamond-fid}
\end{equation}
which ranges from $0$, when the channels have a maximum distance, to  $1$,
when they are exactly equal.

% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a high $f$, while those 
close to unitary channels have much lower $f$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes. \cpnote{Tambien creo qeu debemos comentar que nuestra 
simulación para operaciones unitarias no es optima, porque usamos un monton de compuertas 
y además operaciones doblemente controladas.}
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}
\tbnote{Va}

\begin{figure} % {{{
\centering
\begin{subfigure}{0.9\textwidth}
\begin{subfigure}{.666\textwidth}
\centering
\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
\end{subfigure}%
\begin{subfigure}{.333\textwidth}
\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
\end{subfigure}
\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
\end{subfigure}%
\begin{subfigure}{0.1\textwidth}
\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
\end{subfigure}
\caption{Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
for a sample of Pauli channels in the tetrahedron.  Notice that channels close
to the center of the tetrahedron have high fidelities, while those close to the
borders do not.  Moreover, we show the results for cuts of the tetrahedron at
different values of $\tau_3$.}
\label{fig:fids}
\end{figure} % }}}

@@

\begin{theorem}
Consider a 1PR circuit of $N$ qubits
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
\end{align*}
with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $|a^j|^2 + |b^j|^2 + |c^j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
\cpnote{Sugiero cambiar la a gargoleada por una a con gorro o con tilde. No se 
usa asi cambiar de fuente.}
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
with $B_{i,j}$ the entries of matrix $B$.
This can be rewritten by separating last qubit from the other $N-1$:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{align}
B|j\rangle = 
   \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle 
                                     + B_{2k+1,j} |k \rangle |1\rangle  \right) 
   + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  
                                      + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align}

\cpnote{Separo el parrafo par auqe cada matriz tenga como su propio espacio.}
Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is} |\mathfrak{b}^{j}\rangle + e^{is} |\mathfrak{a}^j\rangle + |\mathfrak{c}^j\rangle
\end{align}
where we defined $|\mathfrak{a}^j \rangle = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
$|\mathfrak{b}^j\rangle = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle$,
$|\mathfrak{c}^j\rangle =\sum_{k \not\in \mathcal{C}}\big( B_{2k,j} |k\rangle|0\rangle+$ $B_{2k+1,j} |k \rangle |1\rangle  \big)$.
\cpnote{Acá puedes usar align. Creo que es mucho para dejarlas en el texto. Recuerda la puntuacion. 
Me está gustando mucho la explicacion. Simple y clara. }
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $|\mathfrak{a}^j|^2 + |\mathfrak{b}^j|^2 + |\mathfrak{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

@@

\cpnote{Acá voy}

@@

%Therefore, from this theorem we conclude that
%the kind of curves of states that can be created
%using a 1PR circuit are always of the form
%\begin{align*}
%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
%\end{align*}
%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
% }}}

\section{1PR circuit for a Pauli map} % {{{
\label{sec: 1PR circuit for a Pauli map}
